%-------------------------
% Resume in Latex
% Author : Jack Coughlin
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage[letterpaper, margin=0.8in]{geometry}
\pagestyle{empty}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{tgpagella}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

%-------------------------------------------
%%%%%%  CONTENT STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\begin{center}
  {\LARGE \textbf{Jack Coughlin}} \

  Master's of Science in Applied Mathematics, Fall 2018
  \vspace{3mm}

  75 Noe Street\ \ \textbullet\ \
  San Francisco, CA

  (206) 245-0838\ \ \textbullet\ \
  johnbcoughlin@gmail.com
\end{center}

%-----------EXPERIENCE-----------------
\hrule
\vspace{-0.4em}
\subsection*{Experience}
\begin{itemize}
  \item
    \headerrow
      {\textbf{Inscriptive, Inc.}}
      {\textbf{San Francisco, CA}}
    \headerrow
      {\emph{Member of Technical Staff}}
      {\emph{2016--2017}}
    \begin{itemize}
      \item
        Developed a standalone anomaly detection service for server monitoring, backed by a new anomaly detection algorithm for time series data, combining Discrete Wavelet analysis with Kernel Density Estimation.
      \item
        Contributed to the creation of a consumer product for inferential statistics on business data.
        Led the integration of statistical techniques into the product as well as key technical implementation and design decisions.
      \item
        Created a high-performance microservices application framework in Java, using gRPC and Kubernetes.
    \end{itemize}
  \item
    \headerrow
      {\textbf{Square, Inc.}}
      {\textbf{San Francisco, CA}}
    \headerrow
      {\emph{Software Engineer}}
      {\emph{2013--2016}}
    \begin{itemize}
      \item
        As part of the Payments team, developed and maintained business-critical Java applications that move millions of dollars daily.
      \item
        Contributed to the development of an automatic reconciliation engine for Square's payment and settlement systems.
    \end{itemize}
\end{itemize}

%-----------EDUCATION-----------------
\hrule
\vspace{-0.4em}
\subsection*{Education}
\begin{itemize}
  \item
    \headerrow
      {\textbf{University of Washington}}
      {\textbf{Seattle, WA}}
    \headerrow
      {\emph{College of Arts and Science}}
      {\emph{2008--2013}}
    \begin{itemize}
      \item B.S. in Mathematics, \emph{magna cum laude}
      \item B.A. in Comparative History of Ideas, \emph{magna cum laude}
  \end{itemize}
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Publications}
\begin{itemize}
  \item
    Multi-scale Anomaly Detection with Wavelets. Jack Coughlin and Gian Perrone, Proceedings of Big Data/Internet of Things. London, UK, 2017.
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Skills}
\begin{indentsection}{\parindent}
  \begin{description*}
    \item[Web Development:] Java, Javascript, HTML, CSS, React, Angular
    \item[Infrastructure:] MySQL, bash, Google Cloud Platform, Kubernetes, gRPC
    \item[Scientific Computing:] Python, Numpy, R, ggplot2, \LaTeX
  \end{description*}
\end{indentsection}

\end{document}
